Double White Dwarf Mergers with CASTRO\\ I. Methodology and Code Verification

### 2015-04-03 papers/wdmerger_I/paper.tex
Add discussion to the paper of the sponge and the hydro boundary conditions.

>>>>

For ghost cells at the physical edge of the domain, we always use quantities 
corresponding to the initial ambient material, to prevent material from raining down
on to the grid in response to the disequilibrium outside the stars. This is an artificial 
choice, but the dynamics outside of the stellar orbit is arbitrary anyway, due to the 
lack of knowledge about the density and velocity field inside this gas. In addition, we employ 
a ``sponge'' similar to that described by \citet{maestro3}. After the hydrodynamics update (but before 
the gravity and rotation correction terms), we apply a damping force to the momentum 
equation as follows:
\begin{equation}
  (\rho \mathbf{u})^{n+1} \to \frac{(\rho \mathbf{u}^{n+1})}{1 + (\Delta t / \Delta t_S) f_S},
\end{equation} 
where $\Delta t_S$ is a timescale for the sponge to operate on, and $f_S$ is the damping factor.
We choose it so that that the sponge is non-operational inside a radius $r_S$ from the origin, and 
fully applied at a radius $r_S^\prime \equiv r_S + \Delta r_S$. We then smooth the sponge 
out between $r_S$ and $r_S^\prime$:
\begin{equation}
  f_{S} = \begin{dcases} 0 & r < r_S \\ \frac{1}{2}\left(1 - \text{cos}\left[\pi\left(\dfrac{r - r_S}{\Delta r_S}\right)\right]\right) & r_S \leq r < r_S^\prime \\ 1 & r \geq r_S^\prime. \end{dcases}
\end{equation}
For the simulations in this paper we set $r_S$ to be 75\% of the distance from the origin to the domain boundaries,
and $\Delta r_S$ so that the sponge extends another 10\% of that distance. We set 
$\Delta t_S = 0.01$ s, which is of the same order as the as the CFL timestep 
for typical problem setups. We find that this sponge is necessary especially in the 
rotating reference frame, as standing instabilities can create very large velocities 
in the ambient fluid that drag down the global timestep by up to an order of magnitude.
However, this provides another reason to distrust the dynamics of the low-density fluid
outside of the stellar orbits.
